Modelling the innovation and extinction of archaeological ideas

### 2018-03-23 analysis/paper/citation-clusters/How-to-cluster-citations.Rmd
add human-labelled citation communities and community groups

```{r}
# If we are resuming the analysis we can just start from here, and read in the data
# frame of citations.
xx <- readRDS( paste0(here::here(), "/analysis/data/derived_data/items_wth_refs.rds"))
length(unique(xx$.out))
```

@@

# network plot of citations: co-citations
library(ggplot2)
library(igraph)
library(ggraph)
library(tidygraph)

@@

@@

>>>>

```{r}
library(ggplot2)
library(igraph)
library(ggraph)
library(tidygraph)

# If we are resuming the analysis we can just start from here, and read in the data
# frame of citations.
xx <- readRDS( paste0(here::here(), "/analysis/data/derived_data/items_wth_refs.rds"))
length(unique(xx$.out))
```

@@

# network plot of citations: co-citations

@@

write_csv(explore_citation_communities,
          here::here('analysis/data/derived_data/explore_citation_communities.csv'))

@@

write_csv(main_authors_in_each_community,
          here::here('analysis/data/derived_data/main_authors_in_each_community.csv'))
